\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for Manipulator Kinematic Obstacle Avoidance

### 2024-03-20 Articles/IROS/root.tex
changed interpolation euations
removed the rotational calculation section

\begin{equation}
	\label{eq: calc rep vel}
	\vec{V}rep_{xyz,ijk} = \mathrm{calc\_rep\_vel}(X[i], Y[j], Z[k]) \quad \forall i, j, k \in \{1, 2\}
\end{equation}

@@

\begin{equation}
	\dot{\vec{q}} = \mathbf{J}^+ \xi_{p} \mathrm{\vec{v}{att}} + \dot{\vec{q}}_{rep}
\end{equation}

@@

\begin{equation} 
	\vec{v} = \frac{\vec{x}_{EE} - \vec{x}_g}{||\vec{x}_{EE} - \vec{x}_g||} \times \frac{\arctan(k_{sigm} \; ||\vec{x}_{EE} - \vec{x}_g||) }{pi/2}
	\label{eq: v_att}
\end{equation}

In Eq.~\ref{eq: v_att}, $\vec{v}$ specifies the end-effector's (EE) translational velocity directed towards the target, integrating both its direction and magnitude. Here, $\vec{x}_{EE}$ represents the EE's current position, and $\vec{x}g$ is the target position, both in Cartesian coordinates. The calculation $\frac{\vec{x}{EE}-\vec{x}g}{||\vec{x}{EE}-\vec{x}g||}$ generates a unit vector pointing towards the target, ensuring targeted movement. The velocity's modulation by the arctangent sigmoid function curtails overshooting by moderating speed in proximity to the target and saturating velocity at a predefined upper limit when distant. The parameter \(k_{sigm}\) in the arctangent function adjusts the curve's steepness, affecting how quickly the end-effector decelerates near the target. A higher \(k_{sigm}\) maintains speed until closer to the target for a sharp deceleration, while a lower value starts slowing down earlier for a gradual approach.

The current orientation of the end-effector (EE) and its goal orientation are encoded through rotation matrices, \(\mathbf{cR}\) for the current state and \(\mathbf{gR}\) for the goal state. The necessary rotational adjustment is identified through the relative rotation matrix \(\mathbf{dR}\), generated by multiplying \(\mathbf{gR}\) with the transpose of \(\mathbf{cR}\) and then normalizing the outcome (eq. \ref{eq: rot_diff_mat}). This process ensures \(\mathbf{dR}\) accurately represents rotational differences, without the effect of any scaling factors.

\begin{equation}
	\mathbf{dR} = \frac{\mathbf{gR} \cdot \mathbf{cR}^{T}}{||\mathbf{gR} \cdot \mathbf{cR}^{T}||}
	\label{eq: rot_diff_mat}
\end{equation}

To enhance computational efficiency and prevent gimbal lock, the approach transitions from matrix to quaternion representations for precise and efficient rotational velocity adjustments, essential for achieving the target orientation of the EE.

The relative rotation matrix is converted into a quaternion, which is subsequently logarithmically transformed. The resulting quaternion's components, excluding the real part, constitute the rotational error vector \( \vec{\omega} \).

\begin{equation}
	\boldsymbol{dR} \mapsto \boldsymbol{dQ} = a + b \, \vec{i} + c \, \vec{j} + d \, \vec{k}
	\label{eq: quat_mapsto}
\end{equation}

\begin{equation}
	\boldsymbol{dQl} = 2 \cdot \log(\boldsymbol{dQ}) = a_{log} + b_{log} \, \vec{i} + c_{log} \, \vec{j} + d_{log} \, \vec{k}
	\label{eq:quat_log}
\end{equation}

\alert{There needs to be an explanation why log, cite: DMP Quaternions article Žlajpah, Ude}

\begin{equation}
	\vec{\omega} =
	\begin{bmatrix}
		b_{log} \\
		c_{log} \\
		d_{log}
	\end{bmatrix}
	\label{eq:rot_error_vector}
\end{equation}

@@

@@

>>>>

\begin{equation}
	\label{eq: calc rep vel}
	\vec{V}rep_{xyz,ijk} = \mathrm{rep}(X[i], Y[j], Z[k]) \quad \forall i, j, k \in \{1, 2\}
\end{equation}

@@

\begin{equation}
	\dot{\vec{q}} = \mathbf{J}^+ \xi_{p} \mathrm{\vec{v}_{att}} + \dot{\vec{q}}_{rep}
\end{equation}

@@

\begin{equation} 
	\vec{v} = \frac{\vec{x}_{EE} - \vec{x}_g}{||\vec{x}_{EE} - \vec{x}_g||} \times \frac{\arctan(k_{sigm} \; ||\vec{x}_{EE} - \vec{x}_g||) }{\pi/2}
	\label{eq: v_att}
\end{equation}

In Eq.~\ref{eq: v_att}, $\vec{v}$ specifies the end-effector's (EE) translational velocity directed towards the target, integrating both its direction and magnitude. Here, $\vec{x}_{EE}$ represents the EE's current position, and $\vec{x}_g$ is the target position, both in Cartesian coordinates. The calculation $\frac{\vec{x}_{EE}-\vec{x}_g}{||\vec{x}_{EE}-\vec{x}_g||}$ generates a unit vector pointing towards the target, ensuring targeted movement. The velocity's modulation by the arctangent sigmoid function curtails overshooting by moderating speed in proximity to the target and saturating velocity at a predefined upper limit when distant. The parameter \(k_{sigm}\) in the arctangent function adjusts the curve's steepness, affecting how quickly the end-effector decelerates near the target. A higher \(k_{sigm}\) maintains speed until closer to the target for a sharp deceleration, while a lower value starts slowing down earlier for a gradual approach.

The current orientation of the end-effector (EE) and its goal orientation are encoded through rotation matrices, \(\mathbf{cR}\) for the current state and \(\mathbf{gR}\) for the goal state. The necessary rotational adjustment is identified through the relative rotation matrix \(\mathbf{dR}\), which is transformed into a quaternion representation, where we than calculate the rotational error using method presented in the article \cite{Zlajpah2017}. 
%
%\begin{equation}
%	\mathbf{dR} = \frac{\mathbf{gR} \cdot \mathbf{cR}^{T}}{||\mathbf{gR} \cdot \mathbf{cR}^{T}||}
%	\label{eq: rot_diff_mat}
%\end{equation}
%
%To enhance computational efficiency and prevent gimbal lock, the approach transitions from matrix to quaternion representations for precise and efficient rotational velocity adjustments, essential for achieving the target orientation of the EE.
%
%The relative rotation matrix is converted into a quaternion, which is subsequently logarithmically transformed. The resulting quaternion's components, excluding the real part, constitute the rotational error vector \( \vec{\omega} \).
%
%\begin{equation}
%	\boldsymbol{dR} \mapsto \boldsymbol{dQ} = a + b \, \vec{i} + c \, \vec{j} + d \, \vec{k}
%	\label{eq: quat_mapsto}
%\end{equation}
%
%\begin{equation}
%	\boldsymbol{dQl} = 2 \cdot \log(\boldsymbol{dQ}) = a_{log} + b_{log} \, \vec{i} + c_{log} \, \vec{j} + d_{log} \, \vec{k}
%	\label{eq:quat_log}
%\end{equation}
%
%\alert{There needs to be an explanation why log, cite: DMP Quaternions article Žlajpah, Ude}
%
%
%
%\begin{equation}
%	\vec{\omega} =
%	\begin{bmatrix}
%		b_{log} \\
%		c_{log} \\
%		d_{log}
%	\end{bmatrix}
%	\label{eq:rot_error_vector}
%\end{equation}

@@

\comment{}{fix units in  plots}

@@

\bibitem{Zlajpah2017}
L. Zlajpah, “On orientation control of functional redundant robots,” in Proc. of the 2017 IEEE International Conference on Robotics and Automation (ICRA), Singapore, May 2017, pp. 2475–2482. doi: 10.1109/ICRA.2017.7989288.
